### 2012-07-04 inst/examples/Reed.Rmd
Reed compared to clark

``` {r  find_dp_opt }
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

q1 <- ggplot(policies, aes(x_grid, x_grid - value)) + xlab("stock size") + ylab=("escapement") 
q1
````

>>>>

``` {r  find_dp_optdet }
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

q1 <- ggplot(policies, aes(x_grid, x_grid - value)) + geom_point() + geom_line() + xlab("stock size") + ylab=("escapement") 
q1
````
